Influence of Connectivity on Dung Beetle Communities

### 2025-04-23 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
some writing

Corridors have been shown to be an important mechanism for facilitating the movement of organisms through fragmented landscapes with the goal of minimizing negative consequences of fragmentation[@haddad_corridor_2003], including decreases in the abundance and diversity of species.

>>>>

Corridors have been shown to be an important mechanism for facilitating the movement of organisms through fragmented landscapes with the goal of minimizing negative consequences of fragmentation[@haddad_corridor_2003].

Corridors are good and generally understood as beneficial for
